Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-02-08 doc/paper.Rmd
additions to intro

As mentioned earlier, subject bias and error rate determination have been a long standing issue in firearm examination \citep{NAS:2009}. For an objective analysis, scientific principle testability and error rate determination are considered to be defining aspects.  Identification of the uncertainities associated with a method of comparison and coming up with a systemized method of quantification, is therefore important. Associating mathematical probabilites in a systematic manner to these methods are one such way of quantification. 
In a previous study conducted by \citet{aoas} a machine learning based algorithm was developed for same source matching of bullets and error rates were discussed using the database from the Hamby Study \citep{hamby}. The method proposed by \citet{chumbley} also provides a means to determine error rates and claims to reduce subject bias. Therefore, giving us a strong motivation to explore the adaptibility of the Chumbley score methodology to bullets. In this paper, we first try to adapt the deterministic algorithm and method developed for toolmarks by \citet{chumbley} to bullets. The method was later improved by \citet{hadler}. After this, we consequently discuss about the efforts in doing so, along with the associated error rates. The data used in this paper also belongs to the Hamby Study \citep{hamby}. This gives us a common platform for comparing the performance of the chumbley method on bullets with an already existing method proposed by \citet{aoas} for bullets. \citet{chumbley}, in their paper, compare two toolmarks with the intention of determining if it comes from the same source (same tool).  \citet{chumbley} used an empirical based setup to validate their proposed algorithm and quantitative method which calculates a U-statisic for the purpose of classification of toolmarks as matching or non-matching. The data for their study was obtained from 50 sequentially manufactured screwdriver tips, and preselected comparison window sizes were given as inputs to the algorithm. The algorithm then compares the two toolmarks and comes up with a U-statistic and an associated p-value to designate them as matches or non-matches. The performance for every 100 comparisons, of the algorithm proposed by \citet{chumbley} and the improvement proposed by \citet{hadler} are listed in the table below.

>>>>

As mentioned earlier, subject bias and error rate determination have been a long standing issue in firearm examination \citep{NAS:2009}. For an objective analysis, scientific principle testability and error rate determination are considered to be defining aspects.  Identification of the uncertainities associated with a method of comparison and coming up with a systemized method of quantification, is therefore important. Associating mathematical probabilites in a systematic manner to these methods are one such way of quantification. 
In a previous study conducted by \citet{aoas} a machine learning based algorithm was developed for same source matching of bullets and error rates were discussed using the database from the Hamby Study \citep{hamby}. The method proposed by \citet{chumbley} also provides a means to determine error rates and claims to reduce subject bias. Therefore, giving us a strong motivation to explore the adaptibility of the Chumbley score methodology to bullets. In this paper, we try to adapt this deterministic algorithm and method developed for toolmarks, to bullets. The method was later improved by \citet{hadler}. After this, we consequently discuss about the efforts in doing so, along with the associated error rates. The data used in this paper also belongs to the Hamby Study \citep{hamby}. This gives us a common platform for comparing the performance of the chumbley method on bullets with the already existing method proposed by \citet{aoas} for bullets. As a brief overview, \citet{chumbley}, in their paper, compare two toolmarks with the intention of determining if it comes from the same source (same tool).  \citet{chumbley} used an empirical based setup to validate their proposed algorithm and quantitative method which calculates a U-statisic for the purpose of classification of toolmarks as matching or non-matching. The data for their study was obtained from 50 sequentially manufactured screwdriver tips, and preselected comparison window sizes were given as inputs to the algorithm. The algorithm then compares the two toolmarks and comes up with a U-statistic and an associated p-value to designate them as matches or non-matches. The performance for every 100 comparisons, of the algorithm proposed by \citet{chumbley} and the improvement proposed by \citet{hadler} are listed in the table below.
